The title

### 2016-10-17 analysis/paper/paper.Rmd
update: Anyathian

Comparing the more complex technologies found in Africa, Europe, the Levant and SW Asia to the simpler chopper/chopping tool technology of Southeast/East Asia, Movius proposed the concept of the Movius Line that separates the Lower Palaeolithic into two cultures - the crude or non- stone tool-making cultures in E and SE Asia (e.g. Imjin/Hantan River Basin, Korea and Luonan Basin and Longyadong Cave, China) and northern China (e.g. Zhoukoudian) and the more complex technologies in Africa, Europe and SW Asia (e.g. Olduvai George Beds, Tanzania and Olorgesailie, Kenya) [@brumm2012biface; @norton2006middle; @gao2014late; @dennell2014hallam].

>>>>

Comparing the more complex technologies found in Africa, Europe, the Levant and SW Asia to the simpler chopper/chopping tool technology of Southeast/East Asia, Movius proposed the concept of the Movius Line that separates the Lower Palaeolithic into two cultures - the simple or non- stone tool-making cultures in E and SE Asia (e.g. Imjin/Hantan River Basin, Korea and Luonan Basin and Longyadong Cave, China) and northern China (e.g. Zhoukoudian) and the more complex technologies in Africa, Europe and SW Asia (e.g. Olduvai George Beds, Tanzania and Olorgesailie, Kenya) [@brumm2012biface; @norton2006middle; @gao2014late; @dennell2014hallam]. In addition, the term "Anyathian" is no longer used, instead the time span in question is referred to as the Middle Pleistocene.
